### 2017-04-22 paper/jfp-submission/evaluation.tex
fiddling with figures..
start typing up investigation of "safe" programs

\begin{figure*}[htp]
\centering
\begin{minipage}{\linewidth}
\centering
\includegraphics[width=0.45\linewidth]{coverage.png}
% \end{minipage}
% \begin{minipage}{\linewidth}
\includegraphics[width=0.45\linewidth]{distrib.png}
\end{minipage}
% \vspace{-8ex}
\caption{Results of our coverage testing and the distribution of test
  outcomes. Our random search successfully finds witnesses for 79--85\% of
  the programs in under one second, improving to 87\% in under
  10 seconds. In both datasets we detect actual type errors about 82\%
  of the time, unbound variables or constructors 3--4\% of the time, and
  diverging loops 2--3\% of the time. For the remaining 11--12\% of the
  programs we are unable to provide any useful feedback.  }
\label{fig:results-witness}
\end{figure*}

@@

@@

% \item \ES{others?}
%
\begin{figure*}[htp]
\centering
\includegraphics[width=0.45\linewidth]{trace_size_step.png}
\includegraphics[width=0.45\linewidth]{trace_size_jump.png}
\caption{Complexity of the generated traces. 81\% of the combined traces
  have a jump complexity of at most 10, with an average complexity of 7
  and a median of 5.}
\label{fig:results-complexity}
\end{figure*}
%
\begin{figure*}[htp]
\centering
\includegraphics[width=0.45\linewidth]{user-study-reason.png}
\includegraphics[width=0.45\linewidth]{user-study-fix.png}
\caption{A classification of students' explanations and fixes for type
  errors, given either \ocaml's error % message
  or \toolname's
  jump-compressed trace. The students given \toolname's jump-compressed
  trace consistently scored better ($\ge 10\%$) than those given \ocaml's type
  error.}
\label{fig:results-user-study}
\end{figure*}

@@

This issue is uncommon in \ocaml\ (we did not detect a single instance
of it across all of our benchmarks), but it would surely be exacerbated
by a language like \haskell, which makes heavy use of overloading. We
suspect that dynamic-symbolic execution would allow us to handle ad-hoc
polymorphism, but defer a proper treatment to future work.

>>>>

\begin{figure}[htp]
\centerline{
\begin{minipage}{1.2\textwidth}
\includegraphics[width=0.5\linewidth]{coverage.png}
% \end{minipage}
% \begin{minipage}{\linewidth}
\includegraphics[width=0.5\linewidth]{distrib.png}
\end{minipage}
}
\vspace{3ex}
\caption{Results of our coverage testing and the distribution of test
  outcomes. Our random search successfully finds witnesses for 79--85\% of
  the programs in under one second, improving to 87\% in under
  10 seconds. In both datasets we detect actual type errors about 82\%
  of the time, unbound variables or constructors 3--4\% of the time, and
  diverging loops 2--3\% of the time. For the remaining 11--12\% of the
  programs we are unable to provide any useful feedback.  }
\label{fig:results-witness}
\end{figure}

@@

\input{safe}

@@

% \item \ES{others?}
%
\begin{figure}[htp]
\centerline{
\begin{minipage}{1.2\textwidth}
\includegraphics[width=0.5\linewidth]{trace_size_step.png}
\includegraphics[width=0.5\linewidth]{trace_size_jump.png}
\end{minipage}
}
\vspace{3ex}
\caption{Complexity of the generated traces. 81\% of the combined traces
  have a jump complexity of at most 10, with an average complexity of 7
  and a median of 5.}
\label{fig:results-complexity}
\end{figure}
%
\begin{figure}[htp]
\centerline{
\begin{minipage}{1.2\textwidth}
\includegraphics[width=0.5\linewidth]{user-study-reason.png}
\includegraphics[width=0.5\linewidth]{user-study-fix.png}
\end{minipage}
}
\vspace{3ex}
\caption{A classification of students' explanations and fixes for type
  errors, given either \ocaml's error % message
  or \toolname's
  jump-compressed trace. The students given \toolname's jump-compressed
  trace consistently scored better ($\ge 10\%$) than those given \ocaml's type
  error.}
\label{fig:results-user-study}
\end{figure}

@@

This issue is uncommon in \ocaml\
(we detected it in around 5\% of our benchmarks),
but it would surely be exacerbated
by a language like \haskell, which makes heavy use of overloading. We
suspect that dynamic-symbolic execution would allow us to handle ad-hoc
polymorphism, but defer a proper treatment to future work.
